Generating Simulated Data

### 2021-04-08 docs/SimData.Rmd
add vonBK pars

# pull observed min and max size from data to optimize start and end bins
minmaxlen <- list()
for(s in names(len_comp_data)){
  minmaxlen[[s]] <- len_comp_data[[s]][[1]] %>%
    dplyr::group_by(species) %>%
    dplyr::summarise(minlen = min(lower.bins, na.rm = TRUE),
                     maxlen = max(upper.bins, na.rm = TRUE)) 
}

@@

binwidths <- function(Lmax, vonBk, Nsizebins){
  #optimal bin size is lower end
  binopt <- 0.23*Lmax^0.6
  #vonBk tells you how many fine bins for fast growth

>>>>

# pull observed min and max size from data to optimize start and end bins
minmaxlen <- list()
# read in saved vonB pars--see if seasons are different and will need a replacement if K wasn't estimated
era <- 1
vonBK <- list()
minmaxvonBK <- list()
for(s in names(len_comp_data)){
  minmaxlendf <- len_comp_data[[s]][[1]] %>%
    dplyr::group_by(species) %>%
    dplyr::summarise(minlen = min(lower.bins, na.rm = TRUE),
                     maxlen = max(upper.bins, na.rm = TRUE))

  vonBKdf <- read.csv(paste0(o.name,"growth_species_NOBA_era",era,"_",s,".csv")) %>%
    rename(par = X) %>%
    pivot_longer(!par, names_to = "species") %>%
    pivot_wider(names_from = par, 
                values_from = value) %>%
    select(species, K)

  minmaxvonBKdf <- left_join(minmaxlendf,vonBKdf)

  minmaxlen[[s]] <- minmaxlendf
  vonBK[[s]] <- vonBKdf
  minmaxvonBK[[s]] <- minmaxvonBKdf

@@

binwidths <- function(Lmin, Lmax, vonBk, Nsizebins){
  #optimal bin size is lower end
  binopt <- 0.23*Lmax^0.6
  #vonBk tells you how many fine bins for fast growth
